### 2021-04-28 treatise-pdflatex/4_simulation.tex
pdflatex: Shrink figure width

In the following, we plot for different values and ratios of \m {N_B, N_{H,t}, N_{H,r}}.
We fix \m {N_R = \RB {3/2} N_B}.
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-small-more-square-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-small-more-wide-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 8, N_{H,r} = 6}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-small-more-tall-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 8}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-big-more-square-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-big-more-wide-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 24, N_{H,r} = 18}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-big-more-tall-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 24}, with \m {6} stages, error.}
\end {figure}

@@

In the following, we plot for \m {N_Y = N_R = 4}, for different ratios of \m {N_{H,t}, N_{H,r}}.
%
\begin {figure} [H]
\includegraphics {error-medium-equal-square-six-usual.png}
\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 8, N_{H,r} = 8}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics {error-medium-equal-wide-six-usual.png}
\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics {error-medium-equal-tall-six-usual.png}
\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
\end {figure}externalfigure

@@

In the following, we plot for \m {N_B = 4}, for different number of stages \m {3} and \m {9}.
We fix \m {N_R = \RB {3/2} N_B} with \m {6} stages again and in the below.
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-three-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {3} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-three-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-three-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {3} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-nine-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {9} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-nine-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-nine-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {9} stages, error.}
\end {figure}

@@

In the following, we plot for different thresholds, for \m {N_B = 4}, focusing on each of OMP, Lasso, DS.
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-six-oommpp.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-six-oommpp.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-six-oommpp.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of OMP, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-six-lasso.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-six-lasso.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-six-lasso.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of Lasso, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-six-ddss.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-six-ddss.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-six-ddss.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of DS, error.}
\end {figure}

@@

When plotting runtime statistics, we only consider the cases where \m {N_{H,t} = N_{H,r} = 3 N_B} with \m {6} stages.
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {time-small-more-square-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {time-medium-more-square-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {time-big-more-square-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
\end {figure}

>>>>

In the following, we plot for different values and ratios of \m {N_B, N_{H,t}, N_{H,r}}.
We fix \m {N_R = \RB {3/2} N_B}.
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-small-more-square-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-small-more-wide-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 8, N_{H,r} = 6}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-small-more-tall-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 8}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-square-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-wide-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-tall-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-big-more-square-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-big-more-wide-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 24, N_{H,r} = 18}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-big-more-tall-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 24}, with \m {6} stages, error.}
\end {figure}

@@

In the following, we plot for \m {N_Y = N_R = 4}, for different ratios of \m {N_{H,t}, N_{H,r}}.
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-equal-square-six-usual.png}
\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 8, N_{H,r} = 8}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-equal-wide-six-usual.png}
\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-equal-tall-six-usual.png}
\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
\end {figure}externalfigure

@@

In the following, we plot for \m {N_B = 4}, for different number of stages \m {3} and \m {9}.
We fix \m {N_R = \RB {3/2} N_B} with \m {6} stages again and in the below.
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-square-three-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {3} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-wide-three-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-tall-three-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {3} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-square-nine-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {9} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-wide-nine-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-tall-nine-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {9} stages, error.}
\end {figure}

@@

In the following, we plot for different thresholds, for \m {N_B = 4}, focusing on each of OMP, Lasso, DS.
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-square-six-oommpp.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-wide-six-oommpp.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-tall-six-oommpp.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of OMP, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-square-six-lasso.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-wide-six-lasso.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-tall-six-lasso.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of Lasso, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-square-six-ddss.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-wide-six-ddss.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {error-medium-more-tall-six-ddss.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of DS, error.}
\end {figure}

@@

When plotting runtime statistics, we only consider the cases where \m {N_{H,t} = N_{H,r} = 3 N_B} with \m {6} stages.
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {time-small-more-square-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {time-medium-more-square-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = 0.8 \textwidth] {time-big-more-square-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
\end {figure}
